SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-14 scipy-1.0/ckdtree.tex
First round of revisions based on reviewer feedback in manuscript PR 39.

% TODO: please check / improve literature citations used here
% what about the time complexity of the kNN implementation?
In 2015, we enhanced \texttt{cKDTree.query} with a $k$ nearest neighbors search
parameter. This may be an efficient operation\cite{Sproull:1991:RNS:3118219.3118331} 
because it generates and returns a data structure that may be only a fraction 
of the size of the full neighbor list. A C++ implementation is provided that releases
the Python global interpreter lock for the neighbor search process, uses
a memory pool to allocate and automatically reclaim \texttt{structs}, and
heapsort to sort the $k$ nearest neighbors distances, even in the case
of periodic boundary conditions. When $k$ is a non-contiguous list of nearest
neighbors to account for (i.e., \texttt{[1, 3, 4]}), the intervening distances
between the nearest neighbor ($k = 1$) and the farthest neighbor requested
are all interrogated, but only those neighbors that are requested are retained
in memory. Thus, the max heap size for this algorithm is conceptually determined
as \texttt{np.arange(max(k))}.

>>>>

% TODO: please check / improve literature citations used here
% what about the time complexity of the kNN implementation?
In 2015, we enhanced \texttt{cKDTree.query} with a $k$ nearest neighbors search
parameter. This is an efficient operation\cite{Sproull:1991:RNS:3118219.3118331} 
because it generates and returns a data structure that may be only a fraction 
of the size of the full neighbor list. A C++ implementation is provided that releases
the Python global interpreter lock for the neighbor search process, uses
a memory pool to allocate and automatically reclaim \texttt{structs}, and
heapsort to sort the $k$ nearest neighbors distances, even in the case
of periodic boundary conditions. When $k$ is a non-contiguous list of nearest
neighbors to account for (i.e., \texttt{[1, 3, 4]}), the intervening distances
between the nearest neighbor ($k = 1$) and the farthest neighbor requested
are all interrogated, but only those neighbors that are requested are retained
in memory. Thus, the maximum heap size for this algorithm is conceptually determined
as \texttt{np.arange(max(k))}.
